Exploring the Types and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-11 thesis/paper.tex
Added notes from meeting

\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}

@@

\textbf{Background  } %Done
The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored. Previous studies have not considered APIs from the perspective of well-established software evolution theories.

@@

@@

%Method
In order to achieve this, an exploratory case study will be undertaken to investigate the underlying motives behind changes to APIs. Empirical analysis of the changes between two major versions of an API will be undertaken, following which, an interview with the architects will be used to validate the findings of our analysis.

@@

\section{Existing Literature} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.

@@

\subsection{Related Work} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.

@@

\section{Case Company Description} \label{case_company_description}
The case company is a company operating in the domain of video surveillance. The company's headquarters are located in Lund, Sweden, with offices in 49 countries worldwide. The company is the global market leader in the markets of network cameras and video encoders. They develop embedded software for security cameras. The cameras are designed to be accessible through APIs that are developed and maintained by the company.

@@

The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study.

@@

%RQ1
The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}. The process followed the decision tree used for the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate. This material was then used as a basis for answering \textbf{RQ1}.

@@

\subsection{RQ1 Results} \label{results_rq1} %Reviewed by JW
\noindent
RQ1: \textbf{How do companies actively drive API evolution?}

>>>>

\title{Exploring the Types and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}

@@

\textbf{Background  } %Give a feeling of the need of this study, answer why Axis needs what is in the Objective (+Context)
The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored. Previous studies have not considered APIs from the perspective of well-established software evolution theories.

@@

%switch places between ^ and v

@@

%Method %wrong tense %include RQs in here %include clear contribution (to johanna)
In order to achieve this, an exploratory case study will be undertaken to investigate the underlying motives behind changes to APIs. Empirical analysis of the changes between two major versions of an API will be undertaken, following which, an interview with the architects will be used to validate the findings of our analysis.

@@

\section{Background} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.

@@

\subsection{API Evolution} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.

@@

\subsection{Case Company Description} \label{case_company_description}
The case company is a company operating in the domain of video surveillance. The company's headquarters are located in Lund, Sweden, with offices in 49 countries worldwide. The company is the global market leader in the markets of network cameras and video encoders. They develop embedded software for security cameras. The cameras are designed to be accessible through APIs that are developed and maintained by the company.

@@

%The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study.

@@

%RQ1
The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}. The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate. This material was then used as a basis for answering \textbf{RQ1}.

@@

\newpage
\newpage
\subsection{RQ1 Results} \label{results_rq1} %Reviewed by JW
\noindent
RQ1: \textbf{How do companies actively drive API evolution?}
